---
title: "Good Feet Review Analysis"
output: html_notebook
---

#1. Exploratory Data Analysis and Preparation

Read in the data
```{r}
gf = read.csv("GF_mkereviews.csv")
str(gf)
```
```{r}
summary(gf)
```
```{r}
gf$review_ID = NULL
```

Randomize the order of the rows
```{r}
gf = gf[sample(nrow(gf), replace = FALSE),]
```

Converting rating to factor
```{r}
gf$review_rating = factor(gf$review_rating)
```

```{r}
library(RColorBrewer)
coul <- brewer.pal(8, "Spectral") 
```
```{r}
barplot(table(gf$review_rating), col=coul)
```
From the barplot we can see that 5 star ratings are in the majority.
```{r}
pie(table(gf$review_rating), col=coul)
```


Create a text corpus from review_text variable. Then clean the corpus, that is convert all tweets to lowercase, stem and remove stop words, punctuation, and additional white spaces. 
```{r}
library(tm)
library(SnowballC)
gf_corpus = VCorpus(VectorSource(gf$review_text))
as.character(gf_corpus[[1]])
```
```{r}
gf_corpus_clean = tm_map(gf_corpus, content_transformer(tolower))
gf_corpus_clean = tm_map(gf_corpus_clean, removeNumbers)
gf_corpus_clean = tm_map(gf_corpus_clean, removeWords, stopwords())

replacePunctuation = function(x){
  gsub("[[:punct:]]+", " ", x)
}

gf_corpus_clean = tm_map(gf_corpus_clean, content_transformer(replacePunctuation))

gf_corpus_clean = tm_map(gf_corpus_clean, stemDocument)
gf_corpus_clean = tm_map(gf_corpus_clean, stripWhitespace)
as.character(gf_corpus_clean[[1]])
```
#2. Word Clouds For 1 Star Reviews vs 5 Star Reviews
```{r}
library(wordcloud)
fivestar = subset(gf, review_rating == "5")$review_text
onestar = subset(gf, review_rating == "1")$review_text
```
```{r}
#fivestar
wordcloud(fivestar, max.words = 100, scale = c(3, 0.5), random.order = FALSE)
```
```{r}
#onestar
wordcloud(fivestar, max.words = 100, scale = c(3, 0.5), random.order = FALSE)
```

Create a document-term matrix from the cleaned corpus. Then split the data into train and test sets. Use 80% of samples (roughly 32925 rows ) for training and the rest for testing.
```{r}

```


