---
title: "Good Feet Review Analysis"
output: html_notebook
---

#1. Exploratory Data Analysis and Preparation

Read in the data
```{r}
gf = read.csv("GF_mkereviews.csv")
str(gf)
```
```{r}
summary(gf)
```
```{r}
gf$review_ID = NULL
```

Randomize the order of the rows
```{r}
gf = gf[sample(nrow(gf), replace = FALSE),]
```

Converting rating to factor with 1-3 stars as bad and 4-5 as good
```{r}
gf$review_rating = factor(gf$review_rating)
levels(gf$review_rating) = list("Good"=c("4", "5"), "Bad"=c("1", "2", "3"))
```

```{r}
library(RColorBrewer)
coul <- brewer.pal(8, "Spectral") 
```
```{r}
barplot(table(gf$review_rating), col=coul, main = "Review Ratings")
```
Converting review_datetime_utc into a Date variable to look at the time series distribution of when reviewers write their reviews to get an idea of when people visit the store the most.
```{r}
gf$years = format(as.Date(gf$review_datetime_utc, format="%m/%d/%Y"), format="%Y")
gf$months = format(as.Date(gf$review_datetime_utc, format="%m/%d/%Y"), format="%m")
```
```{r}
library(car)
coul <- brewer.pal(9, "YlGnBu")
barplot(table(gf$years), col=coul, main="Review Date - Year", las=2)
barplot(table(gf$months), col=coul, main="Review Date - Month", las=2)
```


Create a text corpus from review_text variable. Then clean the corpus, that is convert all tweets to lowercase, stem and remove stop words, punctuation, and additional white spaces. 
```{r}
library(tm)
library(SnowballC)
gf_corpus = VCorpus(VectorSource(gf$review_text))
as.character(gf_corpus[[1]])
```
```{r}
gf_corpus_clean = tm_map(gf_corpus, content_transformer(tolower))
gf_corpus_clean = tm_map(gf_corpus_clean, removeNumbers)
gf_corpus_clean = tm_map(gf_corpus_clean, removeWords, stopwords())

replacePunctuation = function(x){
  gsub("[[:punct:]]+", " ", x)
}

gf_corpus_clean = tm_map(gf_corpus_clean, content_transformer(replacePunctuation))

gf_corpus_clean = tm_map(gf_corpus_clean, stemDocument)
gf_corpus_clean = tm_map(gf_corpus_clean, stripWhitespace)
as.character(gf_corpus_clean[[1]])
```
#2. Word Clouds For 1 Star Reviews vs 5 Star Reviews
```{r}
library(wordcloud)
good = subset(gf, review_rating == "Good")$review_text
bad = subset(gf, review_rating == "Bad")$review_text
```
```{r}
#good
wordcloud(good, max.words = 100, scale = c(3, 0.5), random.order = FALSE)
```
```{r}
#bad
wordcloud(bad, max.words = 100, scale = c(3, 0.5), random.order = FALSE)
```

```{r}
myTdm = as.matrix(TermDocumentMatrix(gf_corpus_clean))
FreqMat = data.frame(ST = rownames(myTdm), 
                     Freq = rowSums(myTdm),
                     row.names=NULL)
#head(FreqMat)
ordered_freq = FreqMat[order(-FreqMat$Freq),]
ordered_freq
```


# 3. Document Term Matrix and Training/Test sets

Create a document-term matrix from the cleaned corpus. Then split the data into train and test sets. Use 80% of samples for training and the rest for testing.
```{r}
gf_dtm = DocumentTermMatrix(gf_corpus_clean)

gf_dtm_train = gf_dtm[1:72, ]
gf_dtm_test = gf_dtm[73:121, ]

gf_train_labels = gf[1:72, ]$review_rating
gf_test_labels = gf[73:121, ]$review_rating
```

```{r}
gf_dtm
```
Removing words that appear no more than five times since our matrix is very sparse. Sparsity = 98%
```{r}
gf_freq_words = findFreqTerms(gf_dtm_train, 5)
gf_dtm_freq_train = gf_dtm_train[, gf_freq_words]
gf_dtm_freq_test = gf_dtm_test[, gf_freq_words]
```
```{r}
gf_dtm_freq_train
```
We will be using Naive Bayes Classifier which takes in categorical features. We will conver the numeric counts of the appearances of a word in document term matrix to "Yes" or "No" to fit these requirements.
```{r}
convert_counts <- function(x) {
x = ifelse(x > 0, "Yes", "No")
}
gf_train = apply(gf_dtm_freq_train, MARGIN = 2,
convert_counts)

gf_test = apply(gf_dtm_freq_test, MARGIN = 2,
convert_counts)
```

# 4. Naive Bayes Classifier

```{r warning=FALSE}
library(caret)
model = train(gf_train, gf_train_labels, "nb", trControl=trainControl(method="cv", number=10, classProbs = TRUE,
summaryFunction = twoClassSummary))
```
```{r}
model
```
```{r message=FALSE, warning=FALSE}
table(predict(model$finalModel, gf_test)$class, gf_test_labels)
```
```{r warning=FALSE}
library(ROCR)
gf_predictions_prob=predict(model, gf_test, type = "prob")
head(gf_predictions_prob)
```
```{r}
pred_yes_gf = prediction(gf_predictions_prob$Good, gf_test_labels)
```
```{r}
performance(pred_yes_gf, measure = "auc")@y.values
```




